---
title: "Homework1"
author: "TS YEAP"
date: "January 20, 2019"
output: html_document
---

Load libraries
```{r message = FALSE}
library(gdata)
library(rvest)
library(htmltab)
```
##Question 1
Import the .xlsx file directly from this url: http://www.huduser.gov/portal/datasets/fmr/fmr2017/FY2017_4050_FMR.xlsx. Include str and dim functions on the imported data set.
```{r}
# the url for the online Excel file
url <- "http://www.huduser.gov/portal/datasets/fmr/fmr2017/FY2017_4050_FMR.xlsx"

# use read.xls to import
data <- read.xls(url, perl = "C:/Perl64/bin/perl.exe")

#show the structure of the data
str(data)

#show the dimention of the data
dim(data)

#show the first few rows and columns of the table
data[1:6, 1:10]
```

##Question 2 & 3
Q2: Scrape Table 3 (Net birth/death estimates by industry supersector) and store in a data frame. Include str and dim functions on your data frame. 

Q3:Scrape Table 4 ( Differences in seasonally adjusted levels ) and store in a data frame. Include str and dim functions on your data frame.. Note you will have to accommodate the double line heading as part of your cleansing
```{r}
#rvest library
webpage <- read_html("http://www.bls.gov/web/empsit/cesbmart.htm")

#extract the tables from the webpage
tbls <- html_nodes(webpage, "table")

#show the head of the tables
head(tbls)
```

```{r}
#empty list to add table data to
tbls_ls <- list()

#Table 3. Net birth/death...
tbls_ls$Table3 <- webpage %>%
        html_nodes("#Table3") %>% 
        html_table() %>%
        .[[1]]

#Table 4. Differences in seasonally...
tbls_ls$Table4 <- webpage %>%
        html_nodes("#Table4") %>% 
        html_table(fill = TRUE) %>%
        .[[1]]

#show the structure of the table list
str(tbls_ls)
```

```{r}
#save Table3 in a variable
table3 <- tbls_ls$Table3

#show the head, structure and dimension of Table 3
head(table3)
str(table3)
dim(table3)
```

```{r}
#save Table4 in a variable
table4 <- tbls_ls$Table4

#show the head of Table 4
head(table4)
```

```{r}
#Double line heading... Further cleansing
#remove row 1 that includes part of the headings
table4 <- table4[-1,]

# rename table headings
colnames(table4) <- c("2017", "Previously_Published_Lvl", "Revised_Lvl", "Diff_Lvl",
                          "Previously_Published_Chg", "Revised_Chg", "Diff_Chg")

#show head, structure and dimension of Table4
head(table4)
str(table4)
dim(table4)
```

##Question 4
Scrape the following table (Sovereign States and Dependency by Population) from https://en.wikipedia.org/wiki/List_of_countries_and_dependencies_by_population  using htmltab. Include str and dim functions on your dataframe. Note you should look at the webpage source code to determine what to include in the which = variable
```{r}
url <- 
  "https://en.wikipedia.org/wiki/List_of_countries_and_dependencies_by_population"
pop <- htmltab(doc = url, which = "//th[text() = 'Rank']/ancestor::table")
head(pop)
str(pop)
dim(pop)
```
