---
title: "Homework2"
author: "TengSiong (T.S) YEAP"
date: "January 23, 2019"
output: html_document
---

####Part 1:Hands-on Replication
**Bar Chart - Fig 4-11**
```{r}
#load the dataset from the url
hotdogs <- read.csv("http://datasets.flowingdata.com/hot-dog-contest-winners.csv",
            sep = ",", header = TRUE)

#inspect the head of the dataset
head(hotdogs)

#Define the color for each bar: if a record has been broken through, 
#fill the color with dark maroon; otherwise, fill the color with light brown
fill_colors <- c()
for ( i in 1:length(hotdogs$New.record) ) {
    if (hotdogs$New.record[i] == 1) {
        fill_colors <- c(fill_colors, "#5D0F0D")
    } else {
        fill_colors <- c(fill_colors, "#e8ca93")
    }
}

#plot the barplot
#1st arg: the hotdogs eaten         2nd arg: specify names for each bar
#3rd arg: color                     4th arg: border (Y/N)
#5th arg: spacing in btw bars       6th and 7th arg: x- and y-axes label
#8th arg: title
barplot(hotdogs$Dogs.eaten, names.arg = hotdogs$Year, col = fill_colors,
          border = NA, space = 0.3, xlab = "Year", 
          ylab = "Hot dogs and buns (HDB) eaten",
        main = "Nathan's Hot Dog Eating Contest Results, 1980-2010")
```

**Stacked bar chart - Fig 4-22**
```{r}
#load the dataset
hot_dog_places <- read.csv('http://datasets.flowingdata.com/hot-dog-places.csv',
                    sep = ",", header = TRUE)

#inspect the head of the dataset
head(hot_dog_places)

#Rename columns to move "X"
names(hot_dog_places) <- c("2000", "2001", "2002", "2003", "2004", "2005", "2006", 
                           "2007", "2008", "2009", "2010")

#inspect the head of the dataset
head(hot_dog_places)

#stacked bar chart requires matrix rather than a df
#convert the df to a matrix
hot_dog_matrix <- as.matrix(hot_dog_places)

#Define colors
stacked_color <- c("#2b1e18", "#9b6c56", "#f0e2a8")

#ylim is to set a limit on y-axes
barplot(hot_dog_matrix, border = NA, space = 0.25, ylim = c(0, 200), 
        col = stacked_color, xlab = "Year", ylab = "Hot dogs and buns (HDBs) eaten",
        main = "Hot Dog Eating Contest Results, 1980-2010")

```

**Scatterplot - Fig 4-28**
```{r}
#load the dataset
subscribers <- read.csv(
                "http://datasets.flowingdata.com/flowingdata_subscribers.csv",
                  sep = ",", header = TRUE)

#inspect dataset
head(subscribers)

#scatterplot - combining both density and points
plot(subscribers$Subscribers, type = "h", ylim = c(0, 30000),
     xlab = "Day", ylab = "Subscribers")
points(subscribers$Subscribers, pch = 19, col = "black")
```

**Time Series - Fig 4-34**
```{r}
#Load the dataset
population <- read.csv("http://datasets.flowingdata.com/world-population.csv",
                       sep = ",", header = TRUE)

#Inspect the dataset
head(population)

#Time series plot
plot(population$Year, population$Population, type = "l", ylim = c(0, 7000000000),
     xlab = "Year", ylab = "Population")
```

**Step chart - Fig 4-43**
```{r}
#Load the dataset
postage <- read.csv("http://datasets.flowingdata.com/us-postage.csv",
                    sep = ",", header = TRUE)

#Inspect the dataset
head(postage)

#Step chart
plot(postage$Year, postage$Price, type="s",
    main="US Postage Rates for Letters, First Ounce, 1991-2010",
    xlab="Year", ylab="Postage Rate (Dollars)")
```
**Loess curve - Fig 4-51**
```{r}
#Load the dataset
unemployment <-read.csv(
  "http://datasets.flowingdata.com/unemployment-rate-1948-2010.csv", sep =",")

#Inspect the dataset
head(unemployment)

#Loess curve
#degree:controls the degree of the polynomials that are fitted
#span: controls how smooth the curve is. 
#The closer the span is to zero, the closer the fit.
scatter.smooth(x = 1:length(unemployment$Value), y = unemployment$Value,
               ylim = c(0,11), degree = 2, col = "#CCCCCC", span = 0.5)
```

####Part 2:Simple Distributions
```{r}
#load the dataset
art <- read.csv("art.csv", header = TRUE, stringsAsFactors = FALSE)
head(art)
```

```{r}
#explore the dimension, structure and summary of the dataset
dim(art)
str(art)
summary(art)
```
*Use the par() function to put all 4 plots in the same plot space (like we did in the lab). Also, give the plots titles, x and y labels, use colors that you like, and if you are using a plot with points, use a symbol you like (pch). In other words, customize these plots to show me that you know how to modify different elements of the plots.*
```{r}
#Due to margin issue, I cannot fit 4 plots in the same plot space.
par(mfrow=c(1,2))

#What is the distribution of total.sale for the whole dataset? 
#Provide two different plots that show two different ways of showing distribution.
plot(sort(art$total.sale), main = "Distribution of Total Sales", type = "l",
     ylab = "Total Sale")
points(sort(art$total.sale), pch = 20, col = "black")

boxplot(art$total.sale ~ art$year ,main = "Total Sale versus Year", 
        xlab = "Year", ylab = "Total Sale")
```

*Next we want to compare the distributions of subsets of total.sales. Use a third of distribution plot (different than what you used for the question above) for both of these plots.*
```{r}
#par(mfrow=c(2,1))
#par() compressed the plots and lost a lot of details.

#What is the distribution of the totals sales for drawing paper?
draw.paper <- art$total.sale[art$paper == "drawing"]
hist(draw.paper, main="Distribution of the Total Sales for Drawing Paper",
     xlab = "Total Sales for Drawing Paper")

#What is the distribution of the totals sales for watercolor paper?
watercolor.paper <- art$total.sale[art$paper == "watercolor"]

d <- density(watercolor.paper)
plot(d, main = "Distribution of the Total Sales for Watercolor Paper",
     xlab = "Total Sales for Watercolor Paper")
polygon(d, col="blue", border="black") 
```